### 2013-01-29 Docs/managing_jobs/managingjobs.tex

>>>>

\section{General Info}

All plotfile directories have a {\tt job\_info} file which lists as
host of parameters about the simulation, including:
\begin{itemize}
\item A descriptive name for the simulation (the {\tt job\_name} runtime
  parameter
\item The number of MPI tasks and OpenMP threads
\item The total amount of CPU-hours used up to this point
\item The data and time of the plotfile creation and the directory it was written to.
\item The build date, machine, and directory
\item The MAESTRO, BoxLib and other relevant git hashes for the source
\item The directories used in the build
\item The compilers used and compilation flags
\item The number of levels and boxes for the grid
\item The properties of the species carried
\item The tolerances for the MG solves
\item The value of all runtime parameters (even those that were not explicitly set in the inputs file)
\end{itemize}
This file makes it easy to understand how to recreate the run that
produced the plotfile.
